An Abstraction-based Approach to Network Synthesis

### 2016-10-14 paper/abstraction/paper.tex
updated abstraction paper outline

\newcommand{\sysname}{{\small \sf Diesel}\xspace}

@@

\title{Abstraction Compilation Techniques}

@@

% Points to make
%
% (1) Lets operators think about topologies/policies at a high-level of abstraction
%     - matches current thinking (e.g., templates)
%
% (2) Promotes a correct-by-construction methodology
%
%     properties that hold over abstract topologies hold over concrete ones
%      - includes correct forwarding behavior
%      - includes reachability (under k-failures)
%
% (3) Enables reusability (e.g., across datacenters) and expansion (e.g., within a datacenter)
%
% (4) lets us scale compilation/algorithms to large-scale topologies

\textbf{Abstract---}
We develop \sysname, a tool for automated reasoning about end-to-end properties of abstract network topologies. \sysname allows network operators to write a centralized routing policy over a high-level abstraction of their network topology. From such a specification, it generates a distributed collection of BGP router configurations that are guaranteed to implement the centralized routing policy for any concrete instantiation of the abstract topology, and for any combination of network failures in the resulting concrete topology.
%
Additionally, properties proven by \sysname over the abstract topology, such as reachability between a source and destination under k-failures, are also guaranteed to hold under any concrete instantiation of the abstract topology.
%
These strong guarantees allow operators to reason about the routing behavior of their network at a high-level abstraction, while also generating an efficient low-level implementation.
%
In addition, operators are able to safely change or expand their network in any way, so long as the new resulting topology also respects the abstraction.
%
We test \sysname out on ... blah blah blah

@@

\begin{easylist}[itemize]
& Network configuration is difficult/error-prone. Operators think of policy at 
  a high level of abstraction, yet implementations:
&& Often configs must be decomposed device-by-device
&& Often need to create reusable configurations for different topologies/policies
&& Ensure different devices/networks kept consistent when policy changes

@@

& To this end, we develop a language called \sysname to simplify the operators task.
&& \sysname allows the operator to define high-level network abstractions to reflect
   the operator's mental model, and then to write a centralized routing policy over the
   abstraction.
&& We develop an intermediate graph-based representation for compiled, abstract policies,
   and show how to compile \sysname policies to this representation. 
&& We develop several algorithms that operate over this graph representation and verify 
   if properties, such as reachability or no black holes under k-failures, are guaranteed
   to hold under any possible concrete instantiation of the network.
&& As a major use-case, we show how the compilation and failure-safety analysis
   of the Propane configuration-synthesis tool can be extended over abstract topologies.
   Explain what Propane is first...
   Our major result is an abstraction theorem, which states that ...
   The result is that policies compiled with the Propane compiler to distributed configurations 
   are guaranteed to have correct forwarding behavior for any possible concrete instantiation 
   of the network, and for any possible combination of failures in the given concrete network.
&&& Finally, we show how abstract compilation makes it possible to dramatically speed up compilation 
    time for the Propane policies, ...
\end{easylist}

@@

%Hence, in this paper, we have two central goals:
%\begin{enumerate}
%\item Foo
%\item Bar
%\end{enumerate}

@@

@@

@@

Placeholder for formal language definition

@@

\begin{easylist}[itemize]
& Define abstractions more formally,
&& e.g., homomorphism between graphs + node/edge constraints

& Give formal semantics of abstract, labelled graph
&& i.e., if a concrete graph + homomorphism is valid
   given an abstract, labelled graph

\end{easylist}

@@

& Show compilation from RIR to Product Graph
&& Note that preferences are general, and it could potentially
   use any implementation (including SDN). But for the sake of 
   simplicity, we will assume a BGP backend like Propane.

& Use the datacenter example from before
&& First define the concretization function for translating the abstract policy
   into the concrete policy
&& Next, show the Product Graphfor both the concrete and abstract policies.

@@

\begin{easylist}[itemize]
& Reachability analysis (i.e., are all locations specified in the policy reachable
  after taking topology into account) 
&& Inference rules for reachability
&& Fixed point computation using SMT solver

& Reachability under k-failures (e.g., aggregation black holes)
&& translation to ILP problem
\end{easylist}

@@

@@

@@

\subsection{Expressiveness}

\begin{easylist}[itemize]
& DCell, BCube, Fattree, others ...
\end{easylist}

@@

\begin{easylist}[itemize]
& Topology abstraction
&& DCell, BCube, Fattree, ...
&& Condor ...

& Configuration automation
& Configuration analysis
& Configuration synthesis
\end{easylist}

>>>>

\newcommand{\sysname}{{\small \sf Propane}\xspace}

@@

\title{An Abstraction-based Approach to Network Synthesis}

@@

% Points to make
%
% (1) Lets operators think about topologies/policies at a high-level of abstraction
%     - matches current thinking (e.g., templates)
%
% (2) Promotes a correct-by-construction methodology
%
%     properties that hold over abstract topologies hold over concrete ones
%      - includes correct forwarding behavior
%      - includes reachability (under k-failures)
%
% (3) Enables reusability (e.g., across datacenters) and expansion (e.g., within a datacenter)
%
% (4) lets us scale synthesis to large-scale topologies

\textbf{Abstract---}
We develop techniques for automated reasoning about end-to-end properties of abstract network topologies. We extend a network synthesis tool, \sysname, to allow network operators to write a high-level routing policy over an abstraction of their network topology. From such a specification, \sysname synthesizes a collection router configurations running the distributed Border Gateway Protocol (BGP) that are guaranteed to implement the centralized routing policy for any concrete instantiation of the abstract topology, and for any combination of network failures in the resulting concrete topology.
%
Additionally, properties proven by \sysname over the abstract topology, such as reachability between a source and destination under k-failures, are also guaranteed to hold under any concrete instantiation of the abstract topology.
%
Something something, expandable/incremental networks. Something something scales compilation to large networks. Something something, templates easier to understand.
%These strong guarantees allow operators to reason about the routing behavior of their network at a high-level abstraction, while also generating an efficient low-level implementation.
%
%In addition, operators are able to safely change or expand their network in any way, so long as the new resulting topology also respects the abstraction.
%
We test \sysname out on ... blah blah blah

@@

\begin{easylist}[itemize]
& Network configuration is difficult/error-prone. Operators think of policy at 
  a high level of abstraction, yet for implementations:
&& Often configs must be decomposed device-by-device
&& Often need to create reusable configurations for different topologies/policies
&& Ensure different devices/networks kept consistent when policy changes

@@

& To this end, we build a language called \sysname to simplify the operators task.
&& \sysname allows the operator to define high-level network abstractions to reflect
   the operator's mental model, and then to write a centralized routing policy over the
   abstraction.
&& We extend the \sysname intermediate graph-based representation to support abstract policies,
   and show how to compile abstract \sysname policies to this representation. 
&& As a major use-case, we show how the compilation and failure-safety analysis
   of the Propane configuration-synthesis tool can be extended over abstract topologies.
&& We develop an abstract interpretation that operates over this graph representation and verifies 
   if properties, such as reachability or k-disjoint paths between two nodes, are guaranteed
   to hold for any possible concrete instantiation of the network.
&& Our major result is an abstraction theorem, which states that ...
&& The result is that policies compiled with the Propane compiler to distributed configurations 
   are guaranteed to have correct forwarding behavior for any possible concrete instantiation 
   of the network, and for any possible combination of failures in the given concrete network.
&&& Finally, we show how abstract compilation makes it possible to dramatically speed up compilation 
    time for the Propane policies, cite some numbers here ... 
\end{easylist}

% Some useful citations from the previous paper listed below

@@

@@

\subsection{Example:  The Backbone}

\begin{easylist}[itemize]
& Example of a backbone network with multiple peers
&& Maybe have a couple of different roles (e.g., special handling to keep traffic in the US)
&& Could show different abstractions here (e.g., one big switch)
&& Could be useful to hint at things to come, e.g., takes 2 sec to compile the abstract one
\end{easylist}

@@

\subsection{Example: The Backbone}

\begin{easylist}[itemize]
& Give the policy over the abstract network
\end{easylist}

@@

Placeholder for formal language definition syntax + semantics

% Examples of code given below

@@

@@

& Show compilation from RIR to Product Graph
&& Note that preferences are general, and it could potentially
   use any implementation (including SDN). But for the sake of 
   simplicity, we will assume a BGP backend like Propane.
\end{easylist}

\begin{easylist}[itemize]
& Define abstractions more formally,
&& e.g., homomorphism between graphs + node/edge constraints
&& Use the datacenter example from before
&& First define the concretization function for translating the abstract policy
   into the concrete policy
&& Next, show the Product Graph for both the concrete and abstract policies.

@@

\begin{easylist}[itemize]
& Graph homomorphism is not enough -- to coarse an overapproximation
&& Use node/edge multiplicites to capture more precise constraints on concrete topologies
&& Show a bunch of examples of fattree, bcube, dcell, hyperX, facebook, google, F10, etc.
& K-disjoint path analysis 
&& Useful for aggregation safety (black holes) & reachability
&& Inference rules as an abstract interpretation using Z3
\end{easylist}

@@

\begin{easylist}
& Extension to \sysname
& lines of code
& optimizations
&& Are there any?
\end{easylist}

@@

\begin{easylist}
& Fattree, F10, Facebook, DCell, BCube, hyperX
& Shortest path routing for each of these topologies but varying different size parameters
\end{easylist}

\subsection{Analysis Precision}

@@

@@

\begin{easylist}[itemize]
& Topologies: DCell, BCube, Fattree, ...
& Topology Abstraction: Condor
& Memory Shape Analysis: Sagiv, others
& Configuration automation
& Configuration analysis
& Configuration synthesis
\end{easylist}
